Finite-state morphological transducers for three Kypchak languages

### 2013-10-24 kipchak-lrec-2013/kipchak-paper.tex
Fran needs to learn how to use booktabs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@48176 72bbbca6-d526-0410-a7d9-f06f51895060

\begin{table}
\begin{center}
\begin{tabular}{|l|rrr|}
		\hline
\multirow{2}{*}{\textbf{Part of speech}} & \multicolumn{3}{|c|}{\textbf{Number of stems}} \\ \cline{2-4}
                        & Kazakh & Tatar & Kumyk \\
		\hline
		Noun & - & - & - \\
		Verb & - & - & - \\
		Adjective & - & - & - \\
		Proper noun & - & - & - \\
		Adverb & - & - & - \\
		Numeral & - & - & - \\
		Conjunction & - & - & - \\
		Postposition & - & - & - \\
		Pronoun & - & - & - \\
		Determiner & - & - & - \\
		\hline
		Total: & - & - & - \\
		\hline
\end{tabular}
 \caption{Number of stems in each of the categories}
 \label{table:coverage}
\end{center}

@@

\begin{table}
\begin{center}
\begin{tabular}{lrr}
\textbf{Language} & \textbf{Precision} & \textbf{Recall} \\
\hline
Kazakh & - &  - \\
Tatar & - & - \\
Kumyk & - & - \\
\hline
\end{tabular}
 \caption{Precision and recall}
 \label{table:coverage}
\end{center}
\end{table}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{lrrr}
		\toprule
\multirow{2}{*}{\textbf{Part of speech}} & \multicolumn{3}{c}{\textbf{Number of stems}} \\ \cline{2-4}
                        & Kazakh & Tatar & Kumyk \\
		\midrule
		Noun & - & - & - \\
		Verb & - & - & - \\
		Adjective & - & - & - \\
		Proper noun & - & - & - \\
		Adverb & - & - & - \\
		Numeral & - & - & - \\
		Conjunction & - & - & - \\
		Postposition & - & - & - \\
		Pronoun & - & - & - \\
		Determiner & - & - & - \\
		\midrule
		Total: & - & - & - \\
		\bottomrule
\end{tabular}
 \caption{Number of stems in each of the categories}
 \label{table:coverage}
\end{center}

@@

\begin{table}
\begin{center}
	\begin{tabular}{lrr}
	\toprule
		\textbf{Language} & \textbf{Precision} & \textbf{Recall} \\
	\midrule
		Kazakh & - &  - \\
		Tatar & - & - \\
		Kumyk & - & - \\
	\bottomrule
	\end{tabular}
	\caption{Precision and recall}
	\label{table:coverage}
\end{center}
\end{table}
